Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/from-weak-separability-to-strong-separability.tex
Reformulated the displays in Case 1
Changed item 4 in poly approx thm for halfspaces I
add experiments

\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
\label{theorem:polynomial-approximation-1}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
multivariate polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil$,
\item $\displaystyle \norm{p} \le \left( 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil \right)^{\frac{1}{2} \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{\frac{1}{\gamma}} \right\rceil}$.
\end{enumerate}
\end{theorem}

@@

\begin{figure}
\begin{center}
\input{figures/pizza-slice}
\end{center}
\caption[]{The figure shows the two regions $R^+$ and $R^-$ used in parts 1 and
2 of
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
parameter $\gamma$. The separating hyperplanes $\ip{v_1}{x} = 0$ and
$\ip{v_2}{x} = 0$ are shown as dashed lines.}
\label{figure:pizza-slice}
\end{figure}

@@

\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
Since the examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_T, y_T)$ are weakly
linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
satisfying \eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

@@

\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{\frac{2}{\gamma}} \right\rceil \; ,
\end{align*}
such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
(resp. $p_i(x) \leq -1/2$).
Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
 and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
\begin{align*}
\norm{p_i} & \le \left(188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; . \\
\end{align*}
By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
\begin{align*}
\norm{c_i}_{\ell_2}
& \le \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil} \; .
\end{align*}
Define vectors $u_i \in \ell_2$ as
\begin{align*}
u_i & = \frac{c_i}{\sqrt{K} \left(376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil \right)^{\frac{1}{2} \lceil \log_2(2K-2) \rceil
\cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}} \; . \\
\end{align*}

>>>>

\begin{theorem}[Polynomial approximation of intersection of halfspaces I]
\label{theorem:polynomial-approximation-1}
Let $v_1, v_2, \dots, v_m \in \R^d$ be vectors such that $\norm{v_1},
\norm{v_2}, \dots, \norm{v_m} \le 1$. Let $\gamma \in (0,1)$. There exists a
multivariate polynomial $p:\R^d \to \R$ such that
\begin{enumerate}
\item $p(x) \ge 1/2$ \\ for all $\displaystyle x \in R^+ = \bigcap_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \ge \gamma \right\}$,
\item $p(x) \le -1/2$ \\ for all $\displaystyle x \in R^- = \bigcup_{i=1}^m \left\{ x \in \B(\zero,1) ~:~  \ip{v_i}{x} \le - \gamma \right\}$,
\item $\displaystyle \deg(p) = \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil$,
\item $\displaystyle \norm{p} \le \left[ 188 \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil \right]^{
  \frac{
    \left\lceil \log_2(2m) \right\rceil \cdot \left\lceil \sqrt{{1}/{\gamma}} \right\rceil
  }{2}
}$.
\end{enumerate}
\end{theorem}

@@

\begin{figure}
\begin{center}
 \scalebox{.65}{\input{figures/pizza-slice}}
\end{center}
\caption[]{The figure shows the two regions $R^+$ and $R^-$ used in parts 1 and
2 of
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
for the case $m=d=2$ and a particular choice of vectors $v_1, v_2$ and margin
parameter $\gamma$. The separating hyperplanes $\ip{v_1}{x} = 0$ and
$\ip{v_2}{x} = 0$ are shown as dashed lines.}
\label{figure:pizza-slice}
\end{figure}

@@

\begin{proof}[Proof sketch of Theorem~\ref{theorem:margin-transformation}]
Since the examples $(x_1, y_1)$,  $\dots$, $(x_T, y_T)$ are weakly
linearly separable with margin $\gamma$, there are vectors $w_1, w_2, \dots, w_K$
satisfying \eqref{equation:weak-linear-separability-1} and
\eqref{equation:weak-linear-separability-2}.

@@

\begin{align*}
\deg(p_i) & = \lceil \log_2(2K-2) \rceil \cdot \left\lceil \sqrt{{2}/{\gamma}} \right\rceil \; ,
\end{align*}
such that all examples $x$ in $R_i^+$ (resp. $R_i^-$) satisfy $p_i(x) \geq 1/2$
(resp. $p_i(x) \leq -1/2$).
Therefore, for all $t=1,2,\dots,T$, if $y_t = i$ then $p_i(x_t) \ge 1/2$,
 and if $y_t \neq i$ then $p_i(x_t) \le -1/2$, and
\begin{align*}
&\norm{p_i} 
\\
& \le 
\left[
  188 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil }{2}
} \; . \\
\end{align*}
By \autoref{lemma:norm-bound}, there exists $c_i \in \ell_2$ such that
$\ip{c_i}{\phi(x)}_{\ell_2} = p_i(x)$, and
\begin{align*}
&\norm{c_i}_{\ell_2}
\\
& \le 
\left[
  376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
\right]^{
  \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil}{2}
} \; .
\end{align*}
Define vectors $u_i \in \ell_2$ as
\begin{align*}
u_i & = 
\frac{c_i/\sqrt{K}}{ 
  \left[
    376 \lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{{2}/{\gamma}} \right \rceil 
  \right]^{
    \frac{\lceil \log_2(2K-2) \rceil \cdot \left \lceil \sqrt{\frac{2}{\gamma}} \right \rceil}{2}
  }
} \; . \\
\end{align*}

### 2019-01-22 ICML-submission/introduction.tex
add experiments

For the case when the examples are weakly linearly separable, it was open for a long 
time whether there exist \textit{efficient} algorithms with finite mistake 
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}. 
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the following question:
is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 
on the dimensionality of the feature vectors? We answer both questions affirmatively by
providing an efficient algorithm with finite dimensionless mistake bound 
(Algorithm~\ref{algorithm:kernelized}) (Note: the second question was previously 
answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm).

>>>>

For the case when the examples are weakly linearly separable, it was open for a long 
time whether there exist \textit{efficient} algorithms with finite mistake 
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}. 
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 
on the dimensionality of the feature vectors? We answer both questions affirmatively by
providing an efficient algorithm with finite dimensionless mistake bound 
(Algorithm~\ref{algorithm:kernelized}) (Note: the second question was previously 
answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm).
